Finding Sigma and Mu

### 2021-08-02 graphs_newt_snakes/find_params.Rmd
I reran the correctted slim script (12 starting points) and the numbers look wild. I also mare the line in params dots and they lined up perfectly.

#2=sigma*sqrt(mu)*2*10^6
y_mu_2 = (2/(sigma*2*10^6))^2
y_mu_5 = (5/(sigma*2*10^6))^2
x_sigma_2 = 2/(sqrt(mu)*2*10^6)
x_sigma_5 = 5/(sqrt(mu)*2*10^6)
ggplot() +
  geom_line(aes(x = sigma, y=y_mu_5), col="blue")+
  geom_line(aes(x = sigma, y=y_mu_2), col="green")+
  geom_line(aes(x = x_sigma_5, y=mu), col="blue")+
  geom_line(aes(x = x_sigma_2, y=mu), col="green")+
  scale_y_log10()+
  #geom_point(data=my_grid[my_grid$results <=2, ], aes(x = Var1, y=Var2), col="green")+
  ggtitle("Value Combinations That Might Work") +
  xlab("Sigma") + ylab("Mu (log)")+ #xlim(0, 0.6)+
  theme_bw()

>>>>

#2=sigma*sqrt(mu)*2*10^6
y_mu_2 = (2/(sigma*2*10^6))^2
y_mu_5 = (5/(sigma*2*10^6))^2
x_sigma_2 = 2/(sqrt(mu)*2*10^6)
x_sigma_5 = 5/(sqrt(mu)*2*10^6)
ggplot() +
  geom_line(aes(x = sigma, y=y_mu_5), col="blue")+
  geom_line(aes(x = sigma, y=y_mu_2), col="green")+
  #lines are out of order, but the points line up. Looks Good!
  #geom_point(aes(x = x_sigma_5, y=mu), col="blue")+
  #geom_point(aes(x = x_sigma_2, y=mu), col="green")+
  scale_y_log10()+
  #geom_point(data=my_grid[my_grid$results <=2, ], aes(x = Var1, y=Var2), col="green")+
  ggtitle("Value Combinations That Might Work") +
  xlab("Sigma") + ylab("Mu (log)")+ #xlim(0, 0.6)+
  theme_bw()
